---
title: "A-19015-2019-12-16"
author: '19015'
date: "2019/12/11"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A-19015-2019-12-16}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions

### 11.1
+ The natural logarithm and exponential functions are inverses of each other, so that mathematically log(exp x) = exp(log x) = x. Show by example that this property does not hold exactly in computer arithmetic. Does the identity hold with near equality? (See all.equal.)

### 11.5
+ Write a function to solve the equation
$$ \frac{2 \Gamma\left(\frac{k}{2}\right)}{\sqrt{\pi(k-1) \Gamma\left(\frac{k-1}{2}\right)}} \int_{0}^{c_{k-1}}\left(1+\frac{u^{2}}{k-1}\right)^{-k / 2} d u = \frac{2 \Gamma\left(\frac{k+1}{2}\right)}{\sqrt{\pi k} \Gamma\left(\frac{k}{2}\right)} \int_{0}^{c_{k}}\left(1+\frac{u^{2}}{k}\right)^{-(k+1) / 2} d u $$
for a, where
$$
c_{k}=\sqrt{\frac{a^{2} k}{k+1-a^{2}}}
$$
Compare the solutions with the points A(k) in Exercise 11.4.

### A-B-O blood type problem

## Answers

### 11.1

+ This property does not hold exactly in computer arithmetic, but the identity holds with near equality.  
```{r}
load('A-19015-2019-12-06.RData')
exp(log(20)) == log(exp(20))
all.equal(exp(log(20)),log(exp(20)))
```

### 11.5
```{r}
# gammaratio <- function(k){
#   if (k %% 2==0) 
#     return(exp(sum(log((k/2-1):1))-sum(log(seq(1,k-3,2)/2))-log(gamma(1/2))))
#   else
#     return(exp(sum(log(seq(1,k-2,2)/2))+log(gamma(1/2))-sum(log(((k-1)/2-1):1))))
# }   ### Gamma ratio computing for large k
# g<- function(a,k){
#   f <- function(x, N) (1 + x^2/N)^(-(N + 1)/2)
#   I1 <- integrate(f,lower = 0,upper = sqrt(a^2*(k-1)/(k-a^2)),rel.tol=.Machine$double.eps^0.25,N = k-1 )$value
#   I2 <- integrate(f,lower = 0,upper = sqrt(a^2*k/(k+1-a^2)),rel.tol=.Machine$double.eps^0.25,N = k )$value
#   return(2*gammaratio(k)*I1/sqrt(k-1)-2*gammaratio(k+1)*I2/sqrt(k))
# }   # the equation in 11.5
# f1 <- function(x,k) pt(sqrt(x^2*(k-1)/(k-x^2)),k-1)-pt(sqrt(x^2*k/(k+1-x^2)),k)
# ##  computing method in 11.4
# a <- seq(0.001,6,0.0001)
# y1 <-numeric(length(a))
# for ( i in 1:length(a)){
#   y1[i] <- g(a[i],100)
# }
plot(cbind(a,y1),type = "l",xlab="a",ylab = "value")
```

+ We can see from the figure there is only one zero point in (0,$\sqrt{k}$).

```{r}
# nk <- c(4:25,100,500,1000)
# ak <-numeric(25)
# qk <-numeric(25)
# for (i in 1:25) {
#   ak[i] <- uniroot(g,c(0.00001,ifelse(nk[i] <=7,sqrt(nk[i])-0.01,2.5)),k=nk[i])$root # the solution of the equation
#   qk[i] <- uniroot(f1,c(0.00001,ifelse(nk[i] <=7,sqrt(nk[i])-0.01,2.5)),k=nk[i])$root # the solution of 11.4
# }
cbind(ak,qk)
plot(cbind(nk,ak),xlab = "k",ylab = "A(k)")
lines(cbind(nk,ak),lwd =2,col = "red")
```

### A-B-O blood type problem
```{r}
# loglike <- function(pq,ng){
#   p <- pq[1]
#   q <- pq[2]
#   r <- 1-p -q
#   a <- c(p^2,q^2,r^2,2*p*r,2*q*r,2*p*q)
#   return(-sum(log(a)*ng))
# }
# na <- 28
# nb <- 24
# noo <- 41
# nab <- 70
# n <-na + nb +noo+nab
# eloglike <- function(pq){
#   p <- pq[1]
#   q <- pq[2]
#   r <- 1-p -q
#   a <- c(p^2+2*p*r,q^2+2*q*r,r^2,2*p*q)
#   ng <- c(na,nb,noo,nab)
#   return(-sum(log(a)*ng))
# }
# r <- sqrt(noo/n)
# f2 <- function(x) x^2 +2*x*r - na/n
# p <- uniroot(f2,c(0,1))$root
# q <- 1-p-r
# m <- 200
# pqr <- matrix(rep(0,m*3),nrow = m)
# ll <- numeric(m)
# pqr[1,]<-c(p,q,r)
# for (i in 2:m) {
#   p <- pqr[i-1,1]
#   q <- pqr[i-1,2]
#   r <- pqr[i-1,3]
#   naa <- p/(p+2*r)*na
#   nao <- 2*r/(p+2*r)*na
#   nbb <- q/(q+2*r)*nb
#   nbo <- 2*r/(q+2*r)*nb
#   ng <- c(naa,nbb,noo,nao,nbo,nab)  #estimation step
#   res <- optim(c(p,q),loglike,method="Nelder-Mead",ng=ng) #maximum step
#   pqr[i,]<-c(res$par,1-res$par[1]-res$par[2])
#   ll[i] <- -eloglike(res$par)
# }
```

+ The final results of p,q,r
```{r}
pqr[200,]
```

+ Solving the log-likelihood directly.
```{r}
# res <- optim(c(p,q),eloglike,method="Nelder-Mead")
res$par
plot(ll[-1],type = "l",ylab = "log-likelihood")
abline(a=ll[200],b=0,col="red")
```

+ According to the figure,the log-maximum likelihood values in M-steps are increasing and converge at last.
