---
title: "Homework2"
author: '19015'
date: "2019/10/12"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A-19015-2019-10-11}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Questions
1 Compute a Monte Carlo estimate of
$$
\int_{0}^{\pi / 3} \sin t d t
$$

2 Use Monte Carlo integration with antithetic variables to estimate
$$
\int_{0}^{1} \frac{e^{-x}}{1+x^{2}} d x
$$
and find the approximate reduction in variance as a percentage of the variance without variance reduction.

3 Obtain the stratified importance sampling estimate in Example 5.13 and compare it with the result of Example 5.10.
Example 5.10 In this example several possible choices of importance functions to estimate
$$
\int_{0}^{1} \frac{e^{-x}}{1+x^{2}} d x
$$
by importance sampling method are compared. 
Now divide the interval (0,1) into five subintervals, (j/5, (j + 1)/5), j = 0, 1, . . . , 4. Then on the jth subinterval variables are generated from the density
$$
\frac{5 e^{-x}}{1-e^{-1}}, \quad \frac{j-1}{5}<x<\frac{j}{5}
$$

## Answers
### 1
  Generate uniform distribution from (0,1)
```{r}
load("A-19015-2019-10-11.RData")
#   set.seed(2333)
# x1<-runif(1000,0,pi/3)
# theta1<-pi/3*mean(sin(x1)) #estimate
# theta1.real<-1-cos(pi/3) #true value

```
  Compare the estimate with the true value
```{r,echo=FALSE}
  c(theta1,theta1.real)
```
### 2
  $Y=f(U_j)$ and $Y'=f(1-U_j)$ are generatlly negatively correlated
```{r}
# f<-function(x) exp(-x)/(1+x^2)
# res2<-sapply(1:1000,FUN = function(o){
#   x2<-runif(1000)
#   MC1<-f(c(x2,runif(1000))) #norm sequence
#   MC2<-f(c(x2,1-x2)) # norm sequence plus reverse sequence
#   c(mean(MC1),mean(MC2))
# })
```

Compare the means and sds
```{r,echo=FALSE}
c(mean(res2[1,]),mean(res2[2,]))
c(sd(res2[1,]),sd(res2[2,]))
```
  
### 3
Divide [0,1] into k intervals. For each j=0,1,..k-1,compute $\hat \theta_j = \int_{j/k}^{(j+1)/k} \frac{e^{-x}}{1+x^{2}} d x$ and $\hat \theta = \sum_0^k \hat \theta_j$. Compared with sd
```{r}
# M<-5000
# N<-1000
# k<-5
# expge<-function(n,a,b){  #Generate r.v.s from [a,b] ~ exp(1)
#   u<-runif(n)
#   x<--log(exp(-a)-(exp(-a)-exp(-b))*u)
#   x
# } 
# 
# res3<-sapply(1:N,FUN = function(o){
#   x<-expge(M,0,1)
#   M1<-mean((1-exp(-1))/(1+x^2))
#   M2<-numeric(k)
#   for (j in 0:(k-1)){
#     a<-j/k
#     b<-(j+1)/k
#     xj<-expge(M/k,a,b)
#     M2[j+1]<-mean((exp(-a)-exp(-b))/(1+xj^2))
#     
#   }
#   c(M1,sum(M2))
# })
c(sd(res3[1,]),sd(res3[2,]))
```
  The results show us that stratifition improved the effiency.