---
title: "A-19015-2019-12-13"
author: "19015"
date: "2019/12/19"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A-19015-2019-12-13}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE,message = FALSE)
```

## P204-3 
+ Question:
  + Use both for loops and lapply() to fit linear models to the mtcars using the formulas stored in this list:
```{r}
formulas <- list(
mpg ~ disp,
mpg ~ I(1 / disp),
mpg ~ disp + wt,
mpg ~ I(1 / disp) + wt
)
```

+ Answer:
```{r}
formu.la <- lapply(formulas,FUN = function(formu) lm(formu,data = mtcars))
summary(formu.la)
formu.loop <- list()
for (i in 1:4)  formu.loop[[i]] <- lm(formulas[[i]],data = mtcars)
summary(formu.loop)

```
  
## P204-4

+ Question:
  + Fit the model mpg ~ disp to each of the bootstrap replicates of mtcars in the list below by using a for loop and lapply(). Can you do it without an anonymous function?
```{r}
bootstraps <- lapply(1:10, function(i) {
rows <- sample(1:nrow(mtcars), rep = TRUE)
mtcars[rows, ]
})
```

+ Answer:
```{r}
boot.loop <- list()
summary(boot.loop)
for (i in 1:4)  boot.loop[[i]] <- lm(mpg ~ disp,data = bootstraps[[i]])
boot.la <- lapply(bootstraps,FUN = function(x) lm(mpg ~ disp,data = x))
summary(boot.la)
lapply(bootstraps,lm,formula= mpg ~ disp)
```

## P204-5

+ Question:
  + For each model in the previous two exercises, extract R2 using the function below.
```{r}
  rsq <- function(mod) summary(mod)$r.squared
```

+ Answers:
```{r}
  lapply(formu.la,rsq)
  lapply(boot.la,rsq)
```


## P214-3

### Question:

+ The following code simulates the performance of a t-test for non-normal data. Use sapply() and an anonymous function to extract the p-value from every trial.
```{r}
trials <- replicate(100,t.test(rpois(10, 10), rpois(7, 10)),simplify = FALSE)
```
Extra challenge: get rid of the anonymous function by using [[ directly.

### Answer:

+  Use sapply() and an anonymous function:
```{r}
sapply(1:100,FUN = function(o) t.test(rpois(10, 10), rpois(7, 10))$p.value)
sapply(trials, '[[',3)
```


## P214-7

### Question:

+ Implement mcsapply(), a multicore version of sapply(). Can you implement mcvapply(), a parallel version of vapply()? Why or why not?

### Answer:
```{r}
  library(parallel)
  cl <- makeCluster(4)
  parSapply(cl,1:100,FUN=function(o){
    x<- rnorm(100)
    mean(x)
  })
  stopCluster(cl)
```
  + vapply can't use for a multi core type, because the FUN.VALUE can't be an environment value.