---
title: "Homework"
author: '19015'
date: "2019/11/12"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{A-19015-2019-11-08}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,warning = FALSE)
```

## Question

### 7.6

+  Efronand Tibshiranidiscuss the scor (bootstrap)test scoredata on 88 students who tookexaminations in ﬁvesubjects [84, Table7.1], [188, Table1.2.1]. The ﬁrst two tests (mechanics, vectors) were closed book and the last three tests (algebra, analysis, statistics) were open book. Each row of the data frame is a set of scores (xi1,...,x i5) for theith student. Use a panel display to display the scatter plots for each pair of test scores. Compare the plot with the sample correlation matrix. Obtain bootstrap estimates of the standard errors for each of the following estimates: ˆ ρ12 =ˆ ρ(mec, vec), ˆ ρ34 =ˆ ρ(alg, ana), ˆ ρ35 =ˆ ρ(alg, sta), ˆ ρ45 =ˆ ρ(ana, sta).
 
### 7.B

+ Repeat Project 7.A for the sample skewness statistic. Compare the coverage rates for normal populations (skewness 0) and χ2(5) distributions (positive skewness).


## Answers

### 7.6

+ Apply bootstrap to scor.
```{r}
load("A-19015-2019-11-08.RData")
# library(bootstrap)
# library(boot)
# set.seed(1234)
# sc<-scor
pairs(sc)
# p.cor<-function(x,i){  ## cor function
#   rr<-cor(x[i,])
#   c(rr[1,2],rr[3,4],rr[3,5],rr[4,5])
# }
# sc.boot<-boot(data = sc,statistic = p.cor,R=2000)
apply(sc.boot$t,2,FUN=sd)
```

## 7.B

+ Conduct a Monte Carlo study to estimate the coverage probabilities under N(0,1),$\mu = 0$
```{r}
# sk <- function(x) {
#   #computes the sample skewness coeff.
#   xbar <- mean(x)
#   m3 <- mean((x - xbar)^3)
#   m2 <- mean((x - xbar)^2)
#   return( m3 / m2^1.5 )
# }
# mu1<-0;n<-1e1;m<-1e3;library(boot);
# boot.sk <- function(x,i) sk(x[i])
# ci1.norm<-ci1.basic<-ci1.perc<-ci1.bca<-matrix(NA,m,2)
# for(i in 1:m){
#   U<-rnorm(n)
#   de <- boot(data=U,statistic=boot.sk, R = 999)
#   ci <- boot.ci(de,type=c("norm","basic","perc","bca"))
#   ci1.norm[i,]<-ci$norm[2:3];ci1.basic[i,]<-ci$basic[4:5]
#   ci1.perc[i,]<-ci$percent[4:5];ci1.bca[i,]<-ci$bca[4:5]
# }
cat('norm =',mean(ci1.norm[,1]<=mu1 & ci1.norm[,2]>=mu1),
    'basic =',mean(ci1.basic[,1]<=mu1 & ci1.basic[,2]>=mu1),
    'perc =',mean(ci1.perc[,1]<=mu1 & ci1.perc[,2]>=mu1),
    'BCa =',mean(ci1.bca[,1]<=mu1 & ci1.bca[,2]>=mu1))
```

+ $\chi^2(5)$,$\mu = \sqrt {8/5}$
```{r}
# mu<-sqrt(8/5)
# ci.norm<-ci.basic<-ci.perc<-ci.bca<-matrix(NA,m,2)
# for(i in 1:m){
#   U<-rchisq(n,5)
#   de <- boot(data=U,statistic=boot.sk, R = 999)
#   ci <- boot.ci(de,type=c("norm","basic","perc","bca"))
#   ci.norm[i,]<-ci$norm[2:3];ci.basic[i,]<-ci$basic[4:5]
#   ci.perc[i,]<-ci$percent[4:5];ci.bca[i,]<-ci$bca[4:5]
# }
cat('norm =',mean(ci.norm[,1]<=mu & ci.norm[,2]>=mu),
    'basic =',mean(ci.basic[,1]<=mu & ci.basic[,2]>=mu),
    'perc =',mean(ci.perc[,1]<=mu & ci.perc[,2]>=mu),
    'BCa =',mean(ci.bca[,1]<=mu & ci.bca[,2]>=mu))

```
